Group 5 Report

### 2022-08-02 Report/Group 5 report.Rmd
Image centred.
fig.align.

```{r}

```

@@

@@

### Details tab

@@

>>>>

@@

<!--Legg inn bilder her-->

@@

### Details tab
```{r dashboard_page_2, out.width="50%", fig.cap="The details tab of the dashboard.", fig.align='center', echo=FALSE}
knitr::include_graphics("Images/Dashboard_page_2.png")
```

@@

```{r dashboard_report_image, echo=FALSE, out.width="50%", fig.align='center'}
knitr::include_graphics("Images/Dashboard_report.png")
```
